### 2018-04-18 paper/algorithm.tex
Adds high-level description of SPOR

\NewScheme{\SPOR}{SPOR}
\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Recv}{Receive}

\NewVariable{\rdv}{rdv}
\NewAlgorithm{\Enc}{Enc}
\NewVariable{\pk}{pk}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Dec}{Dec}
\NewVariable{\sk}{sk}

We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
onion-routed message passing.
\(\SPOR\) provides two algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).

@@

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $m$ is the message to be sent,
      $H_\rdv$ is the onion-route given by the recipient (its first node is the 
      rendez-vous point).
    }
    \Function{\SPOR[\Send]}{$m, H_\rdv$}
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORSend}%
    The algorithm for creating a probabilistic onion route.
    \(d\) is the destination address, \(m\) is the message, \(H_\rdv\) is the 
    header for the rendez-vous point selected by \(d\).%
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H$}
      \State $H\gets \Dec[_\sk][C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat H'\gets H$
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[H'] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORFwd}%
    The forwarding function for a node in a probabilistic onion route.%
  }
\end{figure}

>>>>

\NewScheme{\SPOR}{SPOR}
\NewAlgorithm{\Send}{Send}
\NewAlgorithm{\Fwd}{Forward}
\NewAlgorithm{\Recv}{Receive}

\NewVariable{\rdv}{rdv}
\NewAlgorithm{\Enc}{Enc}
\NewVariable{\pk}{pk}
\NewAlgorithm{\Dec}{Dec}
\NewVariable{\sk}{sk}

We have the Secure Probabilistic Onion Routing scheme, \SPOR, which provides 
onion-routed message passing.
\(\SPOR\) provides two algorithms: \(\SPOR[\Send]\) (\cref{SPORSend}), 
\(\SPOR[\Fwd]\) (\cref{SPORFwd}) and \(\SPOR[\Recv]\) (\cref{SPORRecv}).
Say Alice (sender) wants to send a message \(m\) to Bob (recipient).
Bob uses \(\SPOR[\Recv]\) to create a probabilistic onion route \(H_\rdv\) from 
a rendez-vous point (\(\rdv\) below) to its own device swarm --- all the hops on 
the route are chosen by Bob uniformly at random.
Bob gives \(H_\rdv\) to Alice using an out-of-band channel.
Alice uses \(\SPOR[\Send]\) at some later time to send the message to Bob using 
any of her devices.
\(\SPOR[\Send]\) extends the route \(H_\rdv\) with some hops of Alice's 
choosing, then lets the probabilistic nodes of the route forward the message 
(using \(\SPOR[\Fwd]\)) through to Bob.

@@

\begin{figure}
  \begin{algorithmic}
    \Require{%
      $m$ is the message to be sent,
      $H_\rdv$ is the onion-route given by the recipient (its first node is the 
      rendez-vous point).
    }
    \Function{\SPOR[\Send]}{$m, \pk_D, H_\rdv$}
      \State $H\gets \ExtendRoute[H_\rdv, L, \theta]$
      \State $c_m\gets \Enc[_{\pk_D}][m]$
      \State $D\concat C_H\gets H_\rdv$
      \For{$d\in D$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[c_m, C_H] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORSend}%
    The algorithm for creating a probabilistic onion route.
    \(d\) is the destination address, \(m\) is the message, \(H_\rdv\) is the 
    header for the rendez-vous point selected by \(d\).%
  }
\end{figure}

\begin{figure}
  \begin{algorithmic}
    \Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$c_m, C_H$}
      \State $H\gets \Dec[_\sk][C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[c_m, C_H'] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}
  \caption{\label{SPORFwd}%
    The forwarding function for a node in a probabilistic onion route.%
  }
\end{figure}
